Supporting Information

### 2018-03-30 SupportingInformation.Rmd
modify Ext risk section to include all plots

In addition to [basic unit tests](https://github.com/sghosh89/BIVAN/blob/master/Tests.Rmd), we 
also tested our statistics by testing whether $\cor_l-\cor_u$, $\Ps_l-Ps_u$, and 
$\Dsq_u-\Dsq_u$ revealed the asymmetry of tail dependence known to be present in data simulated
from various copulas. Normal and Frank copula families 
are known to have symmetric tail dependence,
i.e., strengths of dependence in the lower and upper tails are the same, for all copulas
in these families @nelsen2007_copula. Clayton copulas are known to have stronger lower- than 
upper-tail dependence. And survival Clayton copulas, being rotations of Clayton copulas by 
$180^\circ$, have stronger upper- than lower tail dependence @nelsen2007_copula.
Using the `iRho` function from the `copula` package, for each of the four families normal, 
Frank, Clayton, and survival Clayton, we obtained parameters for which the expected value of 
Spearman's $\rho$ was, separately, $0,0.1,0.2,...,0.9$. For each copula family and for each 
of the selected parameter values we generated  $n$ points, 100 times, and thereby computed 100 values of the 
statistics $\cor_l-\cor_u$, $\Ps_l-Ps_u$, and $\Dsq_u-\Dsq_u$. This exercise 
was repeated, separately, 
for $n=1000$ and for $n=35$, these cases being chosen, respectively, to reflect asymptotic behavior of the 
statistics and their behavior on the small datasets which are common in some fields
of ecology. The mean and standard error of the three difference statistics were computed for 
each copula family, parameter value, and value of $n$, and results were plotted against 
Spearman's rho (Figures \ref{fig_stat_testing35} and \ref{fig_stat_testing1000}), 
the expectation being that the difference statistics would be positive for 
Clayton copulas and negative for survival Clayton copulas (except for the case of $\rho=0$, a 
boundary case of these families corresponding to independence), and not significantly different 
from $0$ (we used a $t$-test with a significance threshold of $0.05$) for Frank and normal 
copulas. These expectations were fullfilled (Figures \ref{fig_stat_testing35} and 
\ref{fig_stat_testing1000}).

@@

 *  As expected, when extinction risk calculated after $25$ years, was plotted against each $d$ (=degree of dispersion) we varied, we found that extinction risk was higher for data came from left tail dependent environmental fluctuations than right tail dependent one. With increasing $numlocs$ from $5$ to $25$, extinction risk decreased [for a fixed $d$] but this effect was more prominent in case of data came from right tail-dep environmental noise. [see Figure \ref{fig_risk_r0_numlocs5} - Figure \ref{fig_risk_r0_numlocs25}].

```{r fig_risk_r0_numlocs5, echo=F, cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="LC model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0_numlocs5}", fig.height=4, fig.width=8}
set.seed(seed)
varying_d(numsims=10000,numsteps =25,numlocs=5,r=0,K=100)
```

```{r fig_risk_r0_numlocs25, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="LC model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0_numlocs25}", fig.height=4, fig.width=8}
set.seed(seed)
varying_d(numsims=10000,numsteps =25,numlocs=25,r=0,K=100)
```

@@

  * With increasing $K$ from $100$ to $200$, extinction risk in both case gets decreased as expected. [see Figure \ref{fig_risk_r0.05} - Figure \ref{fig_risk_r0.05_K200}]

 * With increasing $numlocs$ from $5$ to $25$, extinction risk decreased [for a fixed $d$] but this effect was more prominent in case of data came from left tail-dep environmental noise. [see Figure \ref{fig_risk_r1.25} - Figure \ref{fig_risk_r1.25_numlocs25}].

```{r fig_risk_r0.05, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.05}", fig.height=4, fig.width=8}
set.seed(seed)
r<-0.05
numlocs<-5
K<-100
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K)
```

```{r fig_risk_r0.05_K200, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.05_K200}", fig.height=4, fig.width=8}
set.seed(seed)
r=0.05
numlocs<-5
K<-200
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K)
```

```{r fig_risk_r0.25, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.25}", fig.height=4, fig.width=8}
set.seed(seed)
r=0.25
numlocs<-5
K<-100
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K)
```

```{r fig_risk_r0.5, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.5}", fig.height=4, fig.width=8}
set.seed(seed)
r=0.5
numlocs<-5
K<-100
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K)
```

```{r fig_risk_r0.6, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.6}", fig.height=4, fig.width=8}
set.seed(seed)
r=0.6
numlocs<-5
K<-100
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K)
```

```{r fig_risk_r0.7, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.7}", fig.height=4, fig.width=8}
set.seed(seed)
r=0.7
numlocs<-5
K<-100
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K)
```

```{r fig_risk_r0.75, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.75}", fig.height=4, fig.width=8}
set.seed(seed)
r=0.75
numlocs<-5
K<-100
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K)
```

```{r fig_risk_r0.9, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.9}", fig.height=4, fig.width=8}
set.seed(seed)
r=0.9
numlocs<-5
K<-100
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K)
```

```{r fig_risk_r1.0, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.0}", fig.height=4, fig.width=8}
set.seed(seed)
r=1.0
numlocs<-5
K<-100
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K)
```

```{r fig_risk_r1.25, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.25}", fig.height=4, fig.width=8}
set.seed(seed)
r=1.25
numlocs<-5
K<-100
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K)
```

```{r fig_risk_r1.25_numlocs25, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.25_numlocs25}", fig.height=4, fig.width=8}
set.seed(seed)
r=1.25
numlocs<-25
K<-100
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K)
```

```{r fig_risk_r1.5, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.5}", fig.height=4, fig.width=8}
set.seed(seed)
r=1.5
numlocs<-5
K<-100
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K)
```

```{r fig_risk_r1.75, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.75}", fig.height=4, fig.width=8}
set.seed(seed)
r=1.75
numlocs<-5
K<-100
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K)
```

```{r fig_risk_r1.95, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.95}", fig.height=4, fig.width=8}
set.seed(seed)
r=1.95
numlocs<-5
K<-100
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K)
```

>>>>

In addition to [basic unit tests](https://github.com/sghosh89/BIVAN/blob/master/Tests.Rmd), we 
also tested our statistics by testing whether $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and 
$\Dsq_u-\Dsq_u$ revealed the asymmetry of tail dependence known to be present in data simulated
from various copulas. Normal and Frank copula families 
are known to have symmetric tail dependence,
i.e., strengths of dependence in the lower and upper tails are the same, for all copulas
in these families @nelsen2007_copula. Clayton copulas are known to have stronger lower- than 
upper-tail dependence. And survival Clayton copulas, being rotations of Clayton copulas by 
$180^\circ$, have stronger upper- than lower tail dependence @nelsen2007_copula.
Using the `iRho` function from the `copula` package, for each of the four families normal, 
Frank, Clayton, and survival Clayton, we obtained parameters for which the expected value of 
Spearman's $\rho$ was, separately, $0,0.1,0.2,...,0.9$. For each copula family and for each 
of the selected parameter values we generated  $n$ points, 100 times, and thereby computed 100 values of the 
statistics $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and $\Dsq_u-\Dsq_u$. This exercise 
was repeated, separately, 
for $n=1000$ and for $n=35$, these cases being chosen, respectively, to reflect asymptotic behavior of the 
statistics and their behavior on the small datasets which are common in some fields
of ecology. The mean and standard error of the three difference statistics were computed for 
each copula family, parameter value, and value of $n$, and results were plotted against 
Spearman's rho (Figures \ref{fig_stat_testing35} and \ref{fig_stat_testing1000}), 
the expectation being that the difference statistics would be positive for 
Clayton copulas and negative for survival Clayton copulas (except for the case of $\rho=0$, a 
boundary case of these families corresponding to independence), and not significantly different 
from $0$ (we used a $t$-test with a significance threshold of $0.05$) for Frank and normal 
copulas. These expectations were fullfilled (Figures \ref{fig_stat_testing35} and 
\ref{fig_stat_testing1000}).

@@

### LC model :
```{r fig_risk_r0_numlocs5, echo=F, cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="LC model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0_numlocs5}", fig.height=3.5, fig.width=8}
set.seed(seed)
varying_d(numsims=10000,numsteps =25,numlocs=5,r=0,K=50,disp_everywhere=F)
```

```{r fig_risk_r0_numlocs25, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="LC model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0_numlocs25}", fig.height=3.5, fig.width=8}
set.seed(seed)
varying_d(numsims=10000,numsteps =25,numlocs=25,r=0,K=50,disp_everywhere=F)
```

  *  As expected, when extinction risk calculated after $25$ years, was plotted against each $d$ (=degree of dispersion) we varied, we found that extinction risk was higher for data came from left tail dependent environmental fluctuations than right tail dependent one. With increasing $numlocs$ from $5$ to $25$, extinction risk decreased [for a fixed $d$] ; [see Figure \ref{fig_risk_r0_numlocs5} - Figure \ref{fig_risk_r0_numlocs25}].

@@

  * With increasing $K$ from $50$ to $200$, extinction risk in both case gets decreased as expected. [see Figure \ref{fig_risk_r0.05} - Figure \ref{fig_risk_r0.05_K200}]

 * With increasing $numlocs$ from $5$ to $25$, extinction risk decreased [for a fixed $d$] ; [see Figure \ref{fig_risk_r0.05} and Figure \ref{fig_risk_r0.05_numlocs25}].

```{r fig_risk_r0.05, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.05}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.05
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r0.05_K200, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.05_K200}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.05
numlocs<-5
K<-200
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r0.05_numlocs25, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.05_numlocs25}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.05
numlocs<-25
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r0.25, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.25}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.25
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r0.5, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.5}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.5
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r0.6, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.6}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.6
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r0.7, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.7}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.7
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r0.75, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.75}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.75
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r0.9, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.9}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.9
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r1.0, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.0}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-1.0
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r1.25, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.25}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-1.25
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r1.5, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.5}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-1.5
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r1.75, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.75}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-1.75
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r1.95, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.95}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-1.95
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

# Explore equal_dispersal everywhere

    * No effect here.

  * With increasing $K$ from $50$ to $200$, extinction risk in both case gets decreased as expected. [see Figure \ref{fig_risk_r0.05_disp_everywhere} - Figure \ref{fig_risk_r0.05_K200_disp_everywhere}]

 * With increasing $numlocs$ from $5$ to $25$, extinction risk decreased [for a fixed $d$] ; [see Figure \ref{fig_risk_r0.05_disp_everywhere} and Figure \ref{fig_risk_r0.05_numlocs25_disp_everywhere}].

```{r fig_risk_r0.05_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.05_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.05
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r0.05_K200_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal); With increasing K from 50 to 200, extinction risk decreases.\\label{fig_risk_r0.05_K200_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.05
numlocs<-5
K<-200
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r0.05_numlocs25_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal); With increasing numlocs from 5 to 25, extinction risk decreases.\\label{fig_risk_r0.05_numlocs25_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.05
numlocs<-25
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r0.25_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.25_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.25
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r0.5_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.5_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.5
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r0.6_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.6_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.6
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r0.7_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.7_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.7
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r0.75_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.75_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.75
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r0.9_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.9_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.9
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r1.0_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.0_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-1.0
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r1.25_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.25_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-1.25
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r1.5_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.5_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-1.5
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r1.75_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.75_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-1.75
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r1.95_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.95_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-1.95
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```
